The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction

### 2024-02-15 outputs/paper/paper.qmd
finished results section

## National Sample (WVS)
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-corwvs
#| fig-cap: "Correlation Matrix for selected Psychological Constructs measured in World Values Survey USA 1981-2017"
#| fig-width: 10
#| fig-height: 10

@@

final_table <- left_join(wvs_summary_table, correlations, by = "country_code") %>%
  mutate(`Country Name` = countrycode(country_code, "iso3c", "country.name")) %>%
  dplyr::select(`Country Name`, `FW Mean`, correlation, significance, n) %>%
  rename(`Correlation` = correlation) %>%
  mutate(Correlation = paste0(Correlation, significance)) %>% dplyr::select(-significance) %>% 
  arrange(desc(`FW Mean`))
final_table

final_table %>%
  kable("latex", booktabs = T) %>%
  kable_styling(bootstrap_options = "striped") %>%
  footnote(general ="FW Mean = National Average of the Belief in Free Will. \n n.s. p > .05. **p < .01. ***p < .001.") %>% 
  row_spec(which(final_table$`Country Name` == "United States"), background = "#ADD8E6")
```

@@

```{r,include=FALSE,message=FALSE,warning=FALSE}
# inferential statistics age group and freewill
anova_result <- aov(freewill ~ age_group, data =wvs_data_usa  )
summary(anova_result)
model <- lm(job_satisfaction~ freewill * age_group, data = wvs_data_usa)
summary(model)

@@

## Comparison to Amazon Mechanical Turk Sample
```{r}
# Normalize free will scores between the two samples
satisfaction_data_usa_rel_num$freewill_norm <- (satisfaction_data_usa_rel_num$`Belief in Free Will (T1)` - 1)/(6-1)

wvs_data_usa$freewill_norm <- (wvs_data_usa$freewill - 1)/(10-1)

freewill_norm_mean_turk <- mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE)

freewill_norm_mean_wvs <- mean(wvs_data_usa$freewill_norm, na.rm = TRUE)

@@

>>>>

\newpage
## National Sample (WVS)
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-corwvs
#| fig-cap: "Correlation Matrix for selected Psychological Constructs measured in World Values Survey USA 1981-2017"
#| fig-width: 10
#| fig-height: 10

@@

final_table <- left_join(wvs_summary_table, correlations, by = "country_code") %>%
  mutate(`Country Name` = countrycode(country_code, "iso3c", "country.name")) %>%
  dplyr::select(`Country Name`, `FW Mean`, correlation, significance, n) %>%
  rename(`Correlation` = correlation) %>%
  mutate(Correlation = paste0(Correlation, significance)) %>% dplyr::select(-significance) %>% 
  arrange(desc(`FW Mean`))

final_table %>%
  kable("latex", booktabs = T) %>%
  kable_styling(bootstrap_options = "striped") %>%
  footnote(general ="FW Mean = National Average of the Belief in Free Will",
            symbol = "n.s. p > .05. **p < .01. ***p < .001.") %>% 
  row_spec(which(final_table$`Country Name` == "United States"), background = "#ADD8E6")
```

@@

```{r,include=FALSE,message=FALSE,warning=FALSE}

# inferential statistics age group and freewill
anova_result <- aov(freewill ~ age_group, data =wvs_data_usa)
summary(anova_result)
model <- lm(job_satisfaction~ freewill * age_group, data = wvs_data_usa)
summary(model)

@@

## Comparison to Amazon Mechanical Turk Sample
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-comparison
#| tbl-cap: Comparative Summary Statistics Between Amazon MTurk and WVS Samples

# Normalize free will scores between the two samples
satisfaction_data_usa_rel_num$freewill_norm <- (satisfaction_data_usa_rel_num$`Belief in Free Will (T1)` - 1)/(6-1)
satisfaction_data_usa_rel_num$jobsatisfaction_norm <- (satisfaction_data_usa_rel_num$`Job Satisfaction (T1)` - 1)/(7-1)

wvs_data_usa$freewill_norm <- (wvs_data_usa$freewill - 1)/(10-1)
wvs_data_usa$jobsatisfaction_norm <- (wvs_data_usa$job_satisfaction - 1)/(10-1)

# Calculate means and sd of those normalized scores

freewill_norm_mean_turk <- round(mean(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE),2)
freewill_norm_sd_turk <- round(sd(satisfaction_data_usa_rel_num$freewill_norm, na.rm = TRUE),2)
jobsat_norm_mean_turk <- round(mean(satisfaction_data_usa_rel_num$jobsatisfaction_norm, na.rm = TRUE),2)
jobsat_norm_sd_turk <- round(sd(satisfaction_data_usa_rel_num$jobsatisfaction_norm, na.rm = TRUE),2)

freewill_norm_mean_wvs <- round(mean(wvs_data_usa$freewill_norm, na.rm = TRUE),2)
freewill_norm_sd_wvs <- round(sd(wvs_data_usa$freewill_norm, na.rm = TRUE),2)
jobsat_norm_mean_wvs <- round(mean(wvs_data_usa$jobsatisfaction_norm, na.rm = TRUE),2)
jobsat_norm_sd_wvs <- round(sd(wvs_data_usa$jobsatisfaction_norm, na.rm = TRUE),2)

comparative_summary_table <- data.frame(
  "Variable" = c("Belief in Free Will", "Job Satisfaction"),
  "Mean" = c(freewill_norm_mean_turk, jobsat_norm_mean_turk),
  "SD" = c(freewill_norm_sd_turk, jobsat_norm_sd_turk),
  "Mean" = c(freewill_norm_mean_wvs, jobsat_norm_mean_wvs),
  "SD" = c(freewill_norm_sd_wvs,jobsat_norm_sd_wvs),
  check.names = FALSE)

comparative_summary_table %>%
  kable("latex", booktabs = T) %>%
  kable_styling(bootstrap_options = "striped") %>% add_header_above(c(" " = 1, "MTurk Sample" = 2, "WVS Sample" = 2))

t_test_result_fw <- t.test(satisfaction_data_usa_rel_num$freewill_norm, wvs_data_usa$freewill_norm)

t_test_result_js <- t.test(satisfaction_data_usa_rel_num$jobsatisfaction_norm, wvs_data_usa$jobsatisfaction_norm)

@@

Since the two samples use different scales to measure belief in free will and job satisfaction, we normalized the values (mapping it onto a scale from 0 to 1), such that we can compare them directly (@tbl-comparison). Results show that the average rating of free will beliefs is higher in the Amazon Mechanical Turk Sample, than in the national sample (*p* < 0.001, CI [`r t_test_result_fw$conf.int[1]`, `r t_test_result_fw$conf.int[2]`]). The opposite trend can be observed in the ratings of job satisfaction, where the national-level WVS sample has on average higher values (*p* < 0.001, CI [`r t_test_result_js$conf.int[1]`, `r t_test_result_js$conf.int[2]`]).
